First, I would like to thank my advisor, Vishnu Zutshi
for giving me opportunities to make this work possible.
Your mentorship and guidance over the last six years has
contributed to my growth as a scientist and as a person. Thank you
for all the discussions and being patient with me.
I would also like to thank my committee members Michael (Mike) Eads,
Gerald (Jerry) Blazey, and Jeffrey Berryhill for providing feedback
on my dissertation.

For the analysis, I would like to thank Michael (Mike) Eads, for providing
guidance and suggestions throughout the analysis.
I would also like thank Jeffrey Berryhill, Aram Apyan, Jay Lawhorn
and CMS collaboration for their help and guidance.


I would like to thank Alexandre (Sasha) Dychkant for
teaching me various lab equipments and sharing his experimental knowledge.
I would also like to thank
Iman Salehinia, Nicholas Pohlman, Michael Figora, Todd Fletcher,
and Brian Scott who made the instrumentation of
scintillator tile wrapping machine possible.

I would like to thank NIU physics faculty and staff. I would also
like to thank my fellow graduate students
Prudhvi Raj Varma Chintalapati,
Christina Sarosiek,
Brendan Leung,
Aakaash Narayanan,
Osama Mohsen,
Ben Simons,
Wei Hou Tan,
Austin Dick,
Andrew Best,
Prudhvi Nikhil Bhattiprolu,
Will Baker,
Kevin Hamilton,
Jeremiah Mitchell,
and Sebastian Szustkowski
for being great friends.


Lastly, I would like to thank my family for their constant
support and love throughout my time away from home.